### 2022-09-21 AISTATS2023/paper.tex
added synthetic exampls

% If you use natbib package, activate the following three lines:
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}
\bibliographystyle{plainnat}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {./../examples/} }
% If you use BibTeX in apalike style, activate the following line:
%\bibliographystyle{apalike}

@@

The aim of this example is to illustrate the advantages of automatic
bin-splitting based on the objective of Eq.(\ref{eq:opt}). We explore
different setups (black-box functios and dististributions) where, in
each one, we treat as ground-truth the ALE obtained with very dense
sampling. Afterwards, we measure the error of the ALE approximation
with \(K\) fixed-size bins versus the approximation of NAME with
automatic bin-spltting.

\begin{itemize}
\item the biggest bins in regions with constant effect
\item the smallest bins with \(N_k > \tau\), in regions with non-constant effect
\end{itemize}

Prove that (a) this is a good objective, i.e., prove that on average,
this splitting gives the minimum distance from the ground truth ALE
and (b) that DP finds the optimal.

Set-ups:

For limited instances, measure the mean error and std (many seeds)
between gt ALE with uncertainty and approximation with bin-splitting
using (a) fixed-size bins (b) variable-size bins for many \(K\)

for many different \(N_k\)

\begin{itemize}
\item In case where the perfect bin-splitting is served by
  equally-sized bins, DP finds it automatically. Without DP, the user
  should try many different \(K\). and compare them the user's overhead of
  testing many differ
\end{itemize}

For many model-agnostic interpretation techniques
– including interaction detection methods – ground
truth information is usually not available on real-world
data. Therefore, well-constructed simulation experi-
ments with a known ground truth are often used for
empirical evaluations and comparisons, while only one
or few real-world datasets are used to demonstrate
practical applicability (e.g., see Friedman et al. (2008),
Fisher et al. (2019), Goldstein et al. (2015), Greenwell
et al. (2018), or Aas et al. (2021)). Hence, we follow
this commonly used approach to evaluate our method
using various simulation settings.

>>>>

% If you use natbib package, activate the following three lines:
\usepackage[round]{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}
\bibliographystyle{plainnat}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xfrac}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {./../examples/} }
% If you use BibTeX in apalike style, activate the following line:
%\bibliographystyle{apalike}

@@

The aim of this example is to illustrate the advantages of automatic
bin-splitting based on the objective of Eq.(\ref{eq:opt}). For
evaluating our approach, we create the following validation framework;
We generate a big dataset using dense sampling \(N=10^6\) and we treat
as ground-truth the ALE estimation using dense fixed-size binning
\(K=10^3\). Afterwards, we generate less samples \(X=500\) and we
compare (a) the fixed-size ALE estimation for many different \(K\)
versus (b) the auto-bin splitting algorithm. In all cases, the data
generating distribution is \(p(\mathbf{x}) = p(x_2|x_1)p(x_1)\) where
\(x_1 \sim \mathcal{U}(0,1)\),
\(x_2 \sim \mathcal{N}(x_1, \sigma_2^2=2)\).

We denote as
\(\mathcal{Z^{\mathtt{DP}}} = \{z^{\mathtt{DP}}_{k-1}, \cdots,
z^{\mathtt{DP}}_{K}\}\) the sequence obtained by automatic-splitting
based on the optimisation problem of Eq.~(\ref{eq:opt}) and with
\(\mathcal{Z^{\mathtt{K}}}\}\) the corresponding fixed-sized
splitting. The comparison is done using three metrics; (a)
\(\mathcal{L}_{\mathtt{DP|K}}^{\mu} =
\frac{1}{|\mathcal{Z}^{\mathtt{DP|K}}|} \sum_{k=1}^K | \mu_k -
\hat{\mu}_k | \) quantifies the average error in estimating the the
expected effect, (b)
\(\mathcal{L}_{\mathtt{DP|K}}^{\sigma^2} =
\frac{1}{|\mathcal{Z}^{\mathtt{DP|K}}|} \sum_{k=1}^K | \sigma_k^2 -
\hat{\sigma}^2_k | \) the average error in estimating the variance of
the effect and (c)
\(\mathcal{L}^{\rho^2}_{\mathtt{DP|K}} =
\frac{1}{|\mathcal{Z}^{\mathtt{DP|K}}|} \sum_{k=1}^K \rho^2_k \) the
average extra nuisance uncertainty.

\paragraph{Example 1.}

In this example, we defin a black-box function
\(f_1(x_1) = a_1x_1 + x_1x_2\) with 6 piecewise-linear regions of
different-size, i.e., \(a_1\) equals to \(=\{2, -2, 5, -10, 0.5\}\) in
the regions defined by the sequence \(\{0, 0.2, 0.4, 0.45, 0.5,
1\}\). The example highlights the importance of variable-size
splitting. Given that the smalest intervals size is \(0.05\) any
fixed-size splitting with less than \( \frac{1}{\Delta x} = 20\) bins,
will mix together effects and increase the variance error
\(\mathcal{L}_{\mathtt{K}}^{\sigma^2}\) due to the increase of the
residual \(\mathcal{L}_{\mathtt{K}}^{\rho^2} > 0\). This is evident in
figure. On the other hand, a large number of bins divides homogeneuos
regions, i.e. region \([0.5, 1)\), into smaller ones with more
unstable estimations which increases
\(\mathcal{L}_{\mathtt{K}}^{\mu}\) Figure. Variable-size binning leads
to the optimal solution. As we see in figure automatic-bin splitting
small bins in areas with fine-grain effects and merges together
regions with similar effects, leading to a near optimal bin splitting.

\begin{figure}[h]
  \centering
  \includegraphics[width=.23\textwidth]{example_bin_splitting_1/fig_1.jpg}
  \includegraphics[width=.23\textwidth]{example_bin_splitting_1/fig_2.jpg}\\
  \includegraphics[width=.23\textwidth]{example_bin_splitting_1/fig_3.jpg}
  \includegraphics[width=.23\textwidth]{example_bin_splitting_1/fig_4.jpg}
  \caption{Figure 1}
  \label{fig:ex-synth-1-1}
\end{figure}

\paragraph{Example 2.}

The black-box function \(f(\mathbf{x}) = 4x_1^2 + x_2^2 + x_1x_2\)

\begin{figure}[h]
  \centering
  \includegraphics[width=.23\textwidth]{example_bin_splitting_2/fig_1.jpg}
  \includegraphics[width=.23\textwidth]{example_bin_splitting_2/fig_2.jpg}\\
  \includegraphics[width=.23\textwidth]{example_bin_splitting_2/fig_3.jpg}
  \includegraphics[width=.23\textwidth]{example_bin_splitting_2/fig_4.jpg}
  \caption{Figure 1}
  \label{fig:ex-synth-1-1}
\end{figure}
